NumPy---Array Programming in Python

### 2020-01-11 body.tex
Add caption for Fig 3: Proliferation of Arrays

\begin{figure*}
  \centering
  \includegraphics[width=0.8\textwidth]{static/sketches/duck-arrays}
  \caption{\textbf{Proliferation of Arrays.} Many ...}
  \label{fig:array-proliferation}
\end{figure*}

>>>>

\begin{figure*}
  \centering
  \includegraphics[width=0.8\textwidth]{static/sketches/duck-arrays}
  \caption{\textbf{Proliferation of Arrays.} The NumPy array is a classic and simple in-memory representation of array data. Since its inception, numerous other array representations have been developed, including distributed arrays---which are stored on multiple computers, GPU arrays---which utilize graphics processing units for fast computation, computation graphs---which postpone and combine calculations before executing them efficiently, and sparse arrays---which typically contain few non-zero values, and store only those in memory.}
  \label{fig:array-proliferation}
\end{figure*}
